\documentclass[12pt]{article}

\title{Homework 2, Team C}

% Line breaks or "\\" aren't needed in the 
% author section if "\and" is used.
\author{ Jordan Lynn 
\and Ronald Rodriguez 
\and Lance Wells 
\and Brett Menzies
\and 
}

\begin{document}
    \maketitle

\pagebreak

\section{Equip an Item - Brett Menzies}

\textbf{Actors:} \hfil \\ \indent Player \\
\textbf{Preconditions:} \hfil \\ \indent Play has an equitable item, and the necessary skill to use the item \\
\textbf{Summary:} \hfil \\ \indent The Player equips an item, changing their stats appropriately \\
\textbf{Terminates:} \hfil \\ \indent When item is equipped or returned to inventory \\
\textbf{Related use cases:} \hfil \\ \indent Select an Item from Inventory \\
\textbf{Steps:}

\begin{enumerate}
	\item The user Selects an Item from Inventory
	\item The user clicks on an equipment slot on their equipment display.
	\item The system checks if the active item is equitable in that location and the user has the necessary skill.
	\begin{itemize}
		\item If valid: system equips the active item to character and recalculates player stats,
			transporting previously equipped items to inventory if necessary.
		\item If invalid: system prints message in dialog box explaining what conditions failed.
	\end{itemize}
	\item Alternative: The user right-clicks anywhere, deactivating and returning the item to its previous location.
\end{enumerate} 

\hfil \linebreak

\section{Use an Item - Brett Menzies}

\textbf{Actors:} \hfil \\ \indent Player \\
\textbf{Preconditions:} \hfil \\ \indent Player has usable item in inventory, valid target, and necessary skill \\
\textbf{Summary:} \hfil \\ \indent The Player uses his/her skill to use an item on a target \\
\textbf{Terminates:} \hfil \\ \indent After item is consumed or returned to inventory \\
\textbf{Related use cases:} \hfil \\ \indent Select an Item from Inventory \\
\textbf{Steps:}

\begin{enumerate}
	\item The user Selects an Item from Inventory
	\item The user clicks on a target map tile.
	\item The system checks if the target is valid and the user has the necessary skill to use the active item.
	\begin{itemize}
		\item If valid: system applies items effects to target; item is consumed.
		\item If invalid:  system prints message in dialog box explaining what conditions failed.
	\end{itemize}
	\item Alternative: The user right-clicks anywhere, deactivating and returning the item to its previous location.
\end{enumerate} 

\hfil \linebreak

\end{document}
